Figures

### 2021-01-20 figures.Rmd
Update figures.Rmd

```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). (B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C). Red dots indicate sampling sites for fish surveys. (C) Map of study regions (left, Midwest, US; right, Hokkaido, Japan). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}

>>>>

```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). (B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C). Red dots indicate sampling sites for fish surveys. (C) Map of study regions (left, Hokkaido, Japan; right, Midwest, US). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}
